A Quality-of-Content (QoC)-based Joint Source and Channel Coding for Human Detections in A Mobile Surveillance Cloud

### 2015-09-01 draft.tex
Revise

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Xiang Chen, Jenq-Neng Hwang, De Meng, Kuan-Hui Lee, Ricardo L. de Queiroz}   \\
\thanks{This study is partially supported by the “103-EC-17-A-03-S1-214” project from the Ministry of Economic Affairs (MOEA) of Taiwan and “Advanced Wireless Broadband System and Inter-networking Application Technology Development Project” of the Institute for Information Industry which is subsidized by the Ministry of Economy Affairs of Taiwan.}
\thanks{Xiang Chen is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: xchen28@uw.edu).}% <-this % stops a space
\thanks{Jenq-Neng Hwang is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: hwang@uw.edu).}% <-this % stops a space
\thanks{De Meng is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA.}% <-this % stops a space
\thanks{Kuan-Hui Lee is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: ykhlee@uw.edu).}
\thanks{Ricardo L. de Queiroz is with the Department
of Computer Science, Universidade de Brasilia, Brasilia, Brazil (e-mail: queiroz@ieee.org).}

@@

\begin{figure}[t]
\centering{\epsfig{file=Fig/accuracy.eps,width=3.5in}}
\caption{Human detection accuracy with different QPs. The solid line is based on a human detection accuracy model given in Eq. \eqref{eq:accuracy_model}. The RMSE of this curve-fitting is $1.104\%$}\label{fig:accuracy}
\end{figure}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Xiang Chen, Jenq-Neng Hwang, De Meng, Kuan-Hui Lee, Ricardo L. de Queiroz}   \\
\thanks{This study is partially supported by the “103-EC-17-A-03-S1-214” project from the Ministry of Economic Affairs (MOEA) of Taiwan and “Advanced Wireless Broadband System and Inter-networking Application Technology Development Project” of the Institute for Information Industry which is subsidized by the Ministry of Economy Affairs of Taiwan.}
\thanks{Xiang Chen is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: xchen28@uw.edu).}% <-this % stops a space
\thanks{Jenq-Neng Hwang is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: hwang@uw.edu).}% <-this % stops a space
\thanks{De Meng is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA. (e-mail: demeng@uw.edu)}% <-this % stops a space
\thanks{Kuan-Hui Lee is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: ykhlee@uw.edu).}
\thanks{Ricardo L. de Queiroz is with the Department
of Computer Science, Universidade de Brasilia, Brasilia, Brazil (e-mail: queiroz@ieee.org).}

@@

\begin{figure}[t]
\centering{\epsfig{file=Fig/accuracy.eps,width=3.5in}}
\caption{Human detection accuracy with different QPs. The solid line is based on a human detection accuracy model given in Eq. \eqref{eq:accuracy_model}. The RMSE of this curve-fitting is $1.104\%$.}\label{fig:accuracy}
\end{figure}
